\documentclass[10pt,twocolumn]{article}
\usepackage{times}

% Use following instead for LaTex 2.09 (may need some other mods as well).
% \documentstyle[times,twocolumn]{article}

% Set dimensions of columns, gap between columns, and paragraph indent 
\setlength{\textheight}{8.875in}
\setlength{\textwidth}{6.875in}
\setlength{\columnsep}{0.3125in}
\setlength{\topmargin}{0in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\parindent}{1pc}
\setlength{\oddsidemargin}{-.1875in}  % Centers text.
\setlength{\evensidemargin}{-.1875in}

% Add the period after section numbers.  Adjust spacing.
\newcommand{\Section}[1]{\vspace{-8pt}\section{\hskip -1em.~~#1}\vspace{-3pt}} 
\newcommand{\SubSection}[1]{\vspace{-3pt}\subsection{\hskip -1em.~~#1}
     	\vspace{-3pt}}


\begin{document}

% Don't want date printed
\date{}

% Make title bold and 14 pt font (Latex default is non-bold, 16pt) 
\title{\Large\bf My Wonderful Article in IEEE Format}

% For single author (just remove % characters)
%\author{I. M. Anonymous \\
%  My Department \\
%  My Institute \\
%  My City, STATE, zip}

% For two authors (default example)
\author{\begin{tabular}[t]{c@{\extracolsep{8em}}c} 
I. M. Anonymous  & M. Y. Coauthor \\
 \\
        My Department & Coauthor Department \\
        My Institute & Coauthor Institute \\
        City, STATE~~zipcode & City, STATE~~zipcode
\end{tabular}}

\maketitle


\section*{\centering Abstract}

{\em
This is the abstract of my paper.  It must fit within the 
size allowed, which is about 3 inches, including section 
title, which is 11 point bold font.  If you don't want 
the text in italics, simply remove the `em' command and 
the curly braces which bound the abstract text.  If you 
have em commands within an italicized abstract, the text 
will come out as normal (non-italicized) text. 
%end italics mode
}

\Section{Introduction}

Here is my introduction text.  The section heading is in a large
bold font and all sections and subsections are numbered.

Type your main text in 10-point Times, single-spaced at 12pt. Do not
use double-spacing. All paragraphs should be indented 1 pica
(approximately 1/6- or 0.17-inch or 0.422 cm). Be sure your text is
fully justified---that is, flush left and flush right. Please do not
place any additional blank lines between paragraphs.

\SubSection{Previous Work}

There are various bibliographic and citation schemes available in
LaTex, but we choose to use the simplest one in this example.
Throughout I may cite references of the form \cite{key:foo} or
\cite{foo:baz}, and LaTeX will keep track of numbering.  The numbers
are based on the order you place them in the bibliography, not the
order they appear in the text.  They should (I believe) be in
alphabetical order.  LaTex will put square brackets about the number
within the text of your paper.  For those of you new to LaTex, you may
have to run the latex process twice to allow all references to be
resolved. You will get a warning about a missing .aux file.  Just
rerun latex and it will be ok.

\Section{Summary and Conclusions}

This template will get you through the minimum article, i.e., with no
figures or equations.  To include those, please refer to your LaTeX
manual and the IEEE publications guidelines.  However, for a vision
conference you will probably want the following equation somewhere:
$$g(x) = {1\over\sqrt{2\pi}\sigma}e^{-x^2/2\sigma^2}$$
Good Luck!

% This is how to do an unnumbered section (note asterisk).
\section*{Acknowledgments}

This is how to do an unnumbered subsection.  For submission, there
should be no acknowledgments as this could lead to identification
of the author.

\begin{thebibliography}{9}
\small  % Use 9 point text.

\bibitem{key:foo}
I. M. Author,
``Some Related Article I Wrote,''
{\em Some Fine Journal}, Vol. 17, pp. 1-100, 1987.
\bibitem{foo:baz}

A. N. Expert,
{\em A Book He Wrote,}
His Publisher, 1989.

\end{thebibliography}
\end{document}

